---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Fitting Linear Regression Model

**Linearregression** package is used for fitting linear fitting linear regression models with numeric or categorical covariates.

Firstly, *lr()* is used for estimating the linear regression model with similar founctional form below:
$Y_{i} = \beta_{0} + \beta_{1} X_{1i} + \beta_{2} X_{2i}+ \epsilon_{i}$
to the estimated equation below:
$\hat{Y_{i}} = \hat{\beta_{0}} + \hat{\beta_{1}} X_{1i} + \hat{\beta_{2}} X_{2i}$
based on the observation samples of Y and X's.

Secondly, *lr()* will make some inference tests for estimated coefficients: $\hat{\beta_{0}} , \hat{\beta_{1}}$ and $\hat{\beta_{2}}$.

Compared with commonly used *lm()* in package **stats**, the main function *lr()* in **Linearregression** package is more efficient with same accuracy since we used matrix operation function in Rcpp.

The goal of this tutorial is to give a general introduction to **Linearregression** package. It will help to know how to use *lr()* this package and its performance from following aspects:

- Item 1[^1]
- Item 2[^2]
- Item 3[^2]
---------

```{r setup}
library(Linearregression)
```

##[^1]; Data preparing
There are three compatible types of data from Y and X's: vector, matrix and dataframe. In addition, Y must be numeric and X's can be numeric or categorical. For example,
```{r run}
y = c(23, 24, 26, 37, 38, 25, 36, 40)
x1 = c(1, 2, 3, 4, 5, 6, 7, 8)
x2 = c(23, 32, 34, 20, 24, 56, 34, 24)
x3 = c("M", "F", "F", "U", "M", "F", "U", "M")
x4 = mtcars$hp ### using 'mtcars' dataframe from R
```

##[^2]; Arguments and options for *lr()*

There are three compatible types of data from Y and X's: vector, matrix and dataframe. In addition, Y must be numeric and X's can be numeric or categorical. For example,

```{r}
y = c(23, 24, 26, 37, 38, 25, 36, 40)
x1 = c(1, 2, 3, 4, 5, 6, 7, 8)
x2 = c(23, 32, 34, 20, 24, 56, 34, 24)
x3 = c("M", "F", "F", "U", "M", "F", "U", "M")
x4 = mtcars$hp ### using 'mtcars' dataframe from R
```
